Approximation as Differentiation notes

### 2025-02-21 notes/definitions.tex
CMon-enriched category.

A category is $\CMon$-enriched if $\Hom{A}{B}$ is closed under the \emph{zero} morphism $\zero_{A,B}$ and
addition of morphisms $+_{A,B}$ satisfying the commutative monoid laws.

>>>>

A category is $\CMon$-enriched if every $\Hom{A}{B}$ is a commutative monoid with the \emph{zero} morphism
$\zero_{A,B}$ as the unit and addition of morphisms $+_{A,B}$ as the commutative monoid operation.
